---
title: "References"
lightbox: true
format:
  html:
    code-tools: 
      source: true
      toggle: true
    code-fold: true
---

```{r}
#| output: false

source("global.R")
```

## License

Data are available by [CC-0](https://creativecommons.org/share-your-work/public-domain/cc0/) license in accordance with the [Palmer Station LTER Data Policy](https://pallter.marine.rutgers.edu/data/) and the [LTER Data Access Policy for Type I data](https://lternet.edu/data-access-policy/).

## Citation

```{r}
citation("palmerpenguins")
```

## Additional data use information

Anyone interested in publishing the data should contact [Dr. Kristen Gorman](https://www.uaf.edu/cfos/people/faculty/detail/kristen-gorman.php) about analysis and working together on any final products. From Gorman et al. (2014): “Individuals interested in using these data are expected to follow the US LTER Network’s Data Access Policy, Requirements and Use Agreement: <https://lternet.edu/data-access-policy/>.”

To cite the palmerpenguins package, please use:

## References

**Data originally published in:**

-   Gorman KB, Williams TD, Fraser WR (2014). Ecological sexual dimorphism and environmental variability within a community of Antarctic penguins (genus *Pygoscelis*). PLoS ONE 9(3):e90081. <https://doi.org/10.1371/journal.pone.0090081>

**Data citations:**

Adélie penguins:

-   Palmer Station Antarctica LTER and K. Gorman, 2020. Structural size measurements and isotopic signatures of foraging among adult male and female Adélie penguins (*Pygoscelis adeliae*) nesting along the Palmer Archipelago near Palmer Station, 2007-2009 ver 5. Environmental Data Initiative. <https://doi.org/10.6073/pasta/98b16d7d563f265cb52372c8ca99e60f> (Accessed 2020-06-08).

Gentoo penguins:

-   Palmer Station Antarctica LTER and K. Gorman, 2020. Structural size measurements and isotopic signatures of foraging among adult male and female Gentoo penguin (*Pygoscelis papua*) nesting along the Palmer Archipelago near Palmer Station, 2007-2009 ver 5. Environmental Data Initiative. <https://doi.org/10.6073/pasta/7fca67fb28d56ee2ffa3d9370ebda689> (Accessed 2020-06-08).

Chinstrap penguins:

-   Palmer Station Antarctica LTER and K. Gorman, 2020. Structural size measurements and isotopic signatures of foraging among adult male and female Chinstrap penguin (*Pygoscelis antarcticus*) nesting along the Palmer Archipelago near Palmer Station, 2007-2009 ver 6. Environmental Data Initiative. <https://doi.org/10.6073/pasta/c14dfcfada8ea13a17536e73eb6fbe9e> (Accessed 2020-06-08).
